### 2022-04-25 introduction.tex
Implemented feedback from instructor

Solar power production is extremely dependent on weather conditions \cite{lin_temporal_2020, lee_forecasting_2018, jaidee_very_2019, su_machine_2019, jang_solar_2016}. A single cloud can seriously impact the production of a solar farm. Such unreliability in a power production system is highly undesirable since production must match demand \cite{lee_forecasting_2018}. When solar power production falls, the power demand it was serving must be fulfilled by other means. Fossil fueled power plants are generally kept on standby, waiting to fulfil this demand \cite{lee_forecasting_2018}. These plants often take hours to start, generally pollute more than other plants and are very expensive to run \cite{lee_forecasting_2018}.
Reliable and accurate forecasts of the fluctuations in solar power production can give power grid operators notice and insight into future power production \cite{lee_forecasting_2018}. This notice enables planning for the dips in power production and making arrangements for the future. This provides the tools to reduce the cost and pollution of power generation as well as increase the reliability of power delivery to consumers \cite{lee_forecasting_2018}.
Recent advancements in deep learning have unlocked new tools that have been shown to be extremely effective in predicting the future behaviour of a system given enough relevant data.\\

@@

\subsection{LSTMs and GRUs}
\textcolor{blue}{Is there value in going deeper?}\\
Recurrent Neural Networks (RNNs), especially Gated Recurrent Units (GRUs) and Long-Short Term Memory (LSTM) cells \cite{Goodfellow-et-al-2016} along with more advanced derivatives have been shown to be able to achieve good results when trained on previous weather and power generation data \cite{lin_temporal_2020, lee_forecasting_2018, jaidee_very_2019, su_machine_2019}.
RNNs are a class of deep neural networks where nodes are connected in a temporal sequence, allowing the network to learn time-based data efficiently. LSTMs and GRUs are types of RNNs in which, the nodes in the network have additional stored states controlled by the network via mechanisms that use time delays or feedback loops \cite{Goodfellow-et-al-2016, noauthor_recurrent_2021}.\\

@@

>>>>

Solar power production is highly dependent on weather conditions \cite{lin_temporal_2020, lee_forecasting_2018, jaidee_very_2019, su_machine_2019, jang_solar_2016}. A single cloud can adversely impact the production of a solar farm. Such unreliability in a power production system is undesirable since production must match demand \cite{lee_forecasting_2018}. When solar power production falls, the power demand it was serving must be fulfilled by other means. Fossil fueled power plants are generally kept on standby, waiting to fulfil this demand \cite{lee_forecasting_2018}. These plants often take hours to start, generally pollute more than other plants and are expensive to run \cite{lee_forecasting_2018}.
Reliable and accurate forecasts of the fluctuations in solar power production can give power grid operators notice and insight into future power production \cite{lee_forecasting_2018}. This notice enables planning for the dips in power production and making arrangements for the future. This provides the tools to reduce the cost and pollution of power generation as well as increase the reliability of power delivery to consumers \cite{lee_forecasting_2018}.
Recent advancements in deep learning have unlocked new tools that have been shown to be effective in predicting the future behaviour of a system given enough relevant data.\\

@@

\textcolor{red}{TODO: Background on neural networks}\\

\subsection{LSTMs and GRUs}
Recurrent Neural Networks (RNNs), especially Gated Recurrent Units (GRUs) and Long-Short Term Memory (LSTM) cells \cite{Goodfellow-et-al-2016} along with more advanced derivatives have been shown to be able to achieve good results when trained on previous weather and power generation data \cite{lin_temporal_2020, lee_forecasting_2018, jaidee_very_2019, su_machine_2019}.
RNNs are a class of deep neural networks where nodes are connected in a temporal sequence, allowing the network to learn time-based data efficiently. LSTMs and GRUs are types of RNNs in which, the nodes in the network have additional stored states controlled by the network via mechanisms that use time delays or feedback loops \cite{Goodfellow-et-al-2016, noauthor_recurrent_2021}.\\

@@

The thesis is structured as follows. First we talked about the motivations and background in the introduction. Next we cover the methods, the data and tools used to achieve these goals. The proceeding chapter contains the results of the work, and finally we discuss the implications, strengths and flaws of the work, future work and end with conclusions.

### 2022-04-25 methods.tex
Implemented feedback from instructor

\section{Data}
This work relies on two types of data, the ground truth, the measured irradiance at the power station and the input, the irradiance values from high-resolution weather forecasts for the area. The data used spans the 425 days from August 1 2020 to September 30 2021 for the Ituverava solar power station run by Enel S.p.A. in Minas Gerais, Brazil.

\subsection{Irradiance measurements}
The irradiance was measured with seven Kipp \& Zonen CM21 pyranometers placed around the power station. The pyranometers have a reported maximum measurement error of 3\%. For input into the network, the highest and lowest measured values are dropped and the average value of the other five measurements is used. This data is provided with five-minute intervals, but the neural network operates hourly. To downsample the measurement data to an hourly format, we averaged the values for the twenty minutes before and after the top of each hour. Finally, the irradiance values were normalized linearly to the range 0-1 before input into the neural network.
\newpage

\subsection{Forecast Data}
The weather forecast data is provided by Belgingur ehf., Reykjavik, Iceland. We use irradiance values from historical 24-hour weather forecasts generated by their WRF model, discussed in section~\ref{cha:WRF}. The forecasts have a temporal resolution of one hour and a spatial resolution of 2.5km. One of our models uses forecast data from a 3x3 grid centred on the solar power station, and the other model only the data from the centre of the grid. We use two irradiance values from the forecast, the downward irradiance and the downward diffuse irradiance. These irradiance values were normalized linearly to the range 0-1 before input into the neural network.

@@

\subsection{Error metric}
In other work done in this area, multiple error metrics are used. One error metric is used more commonly than others, Mean Absolute Percentage Error (MAPE) \cite{lin_temporal_2020, lee_forecasting_2018, jaidee_very_2019, su_machine_2019}, which is the reason that metric was chosen.
When working with near-zero values MAPE becomes unhelpful as it is calculated by dividing by that near-zero value, so all cases where the irradiance is less than 15\% of the maximum value in the data set are dropped. Hence we do not evaluate early morning or late evening performance.
While a valuable metric, MAPE does not  fully represent the value of the model. Other factors like confidence, discussed in section~\ref{sec:loss_function} and deviance from total irradiance for the day also represent key factors in the usefulness of the model.

@@

        \begin{table}[ht!]
        \begin{center}
        \caption{The full model hyperparameters.
        \label{tab:full_params}}
        \vspace{0.5cm}
        \begin{tabular}{|l|l|}
        \hline
        \textbf{Hyperparameter} & \textbf{Value} \\ \hline
        Learning rate            & 0.01         \\ \hline
        Batch size              & 24            \\ \hline
        Dropout                 & 0.1            \\ \hline
        Hidden size            & 64         \\ \hline
        Hidden continuous size & 8         \\ \hline
        Attention head size    & 1         \\ \hline
        \end{tabular}

@@

        \begin{table}[ht!]
        \begin{center}
        \caption{The limited model hyperparameters.
        \label{tab:lim_params}}
        \vspace{0.5cm}
        \begin{tabular}{|l|l|}
        \hline
        \textbf{Hyperparameter} & \textbf{Value} \\ \hline
        Learning rate            & 0.005         \\ \hline
        Batch size              & 24            \\ \hline
        Dropout                 & 0.1            \\ \hline
        Hidden size            & 40         \\ \hline
        Hidden continuous size & 6         \\ \hline
        Attention head size    & 1         \\ \hline
        \end{tabular}

>>>>

\section{Data}
This work relies on two types of data, \emph{the ground truth}, the measured irradiance at the power station and \emph{the input}, the irradiance values from high-resolution weather forecasts for the area. The data spans the 425 days from August 1st 2020 to September 30th 2021 for the Ituverava solar power station run by Enel S.p.A. in Minas Gerais, Brazil.

\subsection{Irradiance measurements}
The irradiance was measured with seven Kipp \& Zonen CM21 pyranometers placed around the power station. The pyranometers have a reported maximum measurement error of 3\%. For input into the network, the highest and lowest measured values are dropped and the average value of the other five measurements is used. This data is provided with five-minute intervals, but the neural network operates hourly. To downsample the measurement data to an hourly format, we averaged the values for the twenty minutes before and after the top of each hour. Finally, the irradiance values were normalized linearly to the range $0.0-1.0$ before input into the neural network.
\newpage

\subsection{Forecast Data}
The weather forecast data is provided by Belgingur ehf., Reykjavik, Iceland. We use irradiance values from historical 24-hour weather forecasts generated by their WRF model, discussed in Section~\ref{cha:WRF}. The forecasts have a temporal resolution of one hour and a spatial resolution of 2.5km. One of our models uses forecast data from a 3x3 grid centred on the solar power station, and the other model the data from only the centre of the grid. We use two irradiance values from the forecast, the downward irradiance and the downward diffuse irradiance. These irradiance values were normalized linearly to the range $0.0-1.0$ before input into the neural network.

@@

\subsection{Error metric}
In other work done in this area, multiple error metrics are used. One error metric is used more commonly than others, Mean Absolute Percentage Error (MAPE) \cite{lin_temporal_2020, lee_forecasting_2018, jaidee_very_2019, su_machine_2019}, which is the reason that metric was chosen.
When working with near-zero values MAPE becomes unhelpful as it is calculated by dividing by that near-zero value, so all cases where the irradiance is less than 15\% of the maximum value in the data set are dropped. Hence we do not evaluate early morning or late evening performance.
While a valuable metric, MAPE does not  fully represent the value of the model. Other factors like confidence, discussed in Section~\ref{sec:loss_function} and deviance from total irradiance for the day also represent key factors in the usefulness of the model.

@@

        \begin{table}[ht!]
        \begin{center}
        \caption{The full model hyperparameters.
        \label{tab:full_params}}
        \vspace{0.5cm}
        \begin{tabular}{|l|r|}
        \hline
        \textbf{Hyperparameter} & \textbf{Value} \\ \hline
        Learning rate            & 0.01         \\ \hline
        Batch size              & 24            \\ \hline
        Dropout                 & 0.1            \\ \hline
        Hidden size            & 64         \\ \hline
        Hidden continuous size & 8         \\ \hline
        Attention head size    & 1         \\ \hline
        \end{tabular}

@@

        \begin{table}[ht!]
        \begin{center}
        \caption{The limited model hyperparameters.
        \label{tab:lim_params}}
        \vspace{0.5cm}
        \begin{tabular}{|l|r|}
        \hline
        \textbf{Hyperparameter} & \textbf{Value} \\ \hline
        Learning rate            & 0.005         \\ \hline
        Batch size              & 24            \\ \hline
        Dropout                 & 0.1            \\ \hline
        Hidden size            & 40         \\ \hline
        Hidden continuous size & 6         \\ \hline
        Attention head size    & 1         \\ \hline
        \end{tabular}

### 2022-04-25 results.tex
Implemented feedback from instructor

\chapter{Results}
Both models showed a strong ability to predict solar irradiance one day into the future.
The full model, using weather forecast data from the surrounding area, showed both a lower Mean Absolute Percentage Error (MAPE), at 13.21\% vs. 15.98\%, as well as better tracking in challenging conditions and a better ability to recognize uncertain conditions, generally reporting lower confidence when its predictions were wrong. Both models can be trained to achieve slightly lower MAPE, but that came at the cost of a higher tendency to underfit variance, and higher false confidence.
We show irradiance plots for select days representative of the models' performance in various conditions. These plots show the measured irradiance for the day, the models' predicted irradiance values, along with a 90\% confidence interval, detailed in section~\ref{sec:loss_function}. The plots also show the forecast downward shortwave irradiance, the largest factor in measured irradiance, from the model input. Additionally, the graphs contain the average MAPE for the day and the sum of prediction and observation values. The sum values act as a gauge for the total irradiance for the day.

\section{Full model}
The full model, utilizing irradiance data from surrounding areas achieved an average MAPE of 13.21\% on the test dataset. The maximum daily average MAPE was 138.87\% and the minimum was 2.50\%. 
\begin{figure}[ht!]
    \centering
    \includegraphics[scale=0.75]{imgs/graphs/full/days_full.png}
    \caption{The recorded Mean Absolute Percentage Error (MAPE) for each day in the test dataset for the full model. 
    \label{fig:days_full}}
\end{figure}

\subsection{Low variance days}
In the test dataset, there are some clear days, where the sun was mostly or entirely unobstructed. The model predicted most of these days with very low error, in the range of 2-5\%. The 90\% confidence interval stayed within $\pm100 W/m^2$ for the whole day and the true prediction was almost spot-on, as can be seen in Fig.~\ref{fig:full_low_best}.
\begin{figure}[ht!]
    \centering
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/low/best_3.png}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/low/best_2.png}}\qquad
    \caption{Examples of clear days where the model preformed very well.
    \label{fig:full_low_best}}
\end{figure}

The model did not manage near-perfect predictions on all of these clear days, and made a few under-predictions, as can be seen in Fig.~\ref{fig:full_low_worst}.
These predictions were still even and within the 90\% confidence interval, which was slightly larger than for the other clear day predictions. These predictions had a higher MAPE of 10-13\%.
\begin{figure}[ht!]
    \centering
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/low/worst_1.png}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/low/worst_2.png}}\qquad
    \caption{Examples of clear days where the model did not perform well.
    \label{fig:full_low_worst}}
\end{figure}

\subsection{Medium variance days}
On days with some variance in the irradiance measured, the model was generally able to predict the irradiance with relatively good accuracy.
The model tends to give a smoother prediction than the measured value, averaging through the peaks and valleys of the measured values and most of the time the observed value was within the 90\% confidence interval.

Fig.~\ref{fig:full_med_best} shows examples of good predictions with high confidence, though the confidence is generally lower the farther the irradiance is from the value of a clear day.
\begin{figure}[ht!]
    \centering
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/medium/med_g_1.png}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/medium/med_g_2.png}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/medium/med_g_3.png}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/medium/med_g_4.png}}\qquad
    \caption{Examples of days with some drops in irradiance, where the model performed very well.
    \label{fig:full_med_best}}
\end{figure}

In Fig.~\ref{fig:full_med_med} we can see examples of days where the model achieves higher error, MAPE in the range 19-35\%, but with generally larger 90\% confidence intervals so the model still keeps the measured values close to or within them.
\begin{figure}[ht!]
    \centering
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/medium/med_m_1.png}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/medium/med_m_2.png}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/medium/med_m_3.png}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/medium/med_m_4.png}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/medium/med_m_5.png}}\qquad
    \caption{Examples of days with some drops in irradiance, where the model performed somewhat well.
    \label{fig:full_med_med}}
\end{figure}

For a few medium variance days, the model did not track well. Figs.~\ref{fig:full_med_bad_a} and \ref{fig:full_med_bad_d} show where the model predicted a constant lower irradiance when half the day had high irradiance and the other half low. Figs.~\ref{fig:full_med_bad_b} and \ref{fig:full_med_bad_c} show the model predicting a mostly or fully  sunny day when it wasn't. In all of these cases, the observed irradiance was far outside the 90\% confidence interval.
\begin{figure}[ht!]
    \centering
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/medium/med_b_1.png}\label{fig:full_med_bad_a}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/medium/med_b_2.png}\label{fig:full_med_bad_b}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/medium/med_b_3.png}\label{fig:full_med_bad_c}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/medium/med_b_4.png}\label{fig:full_med_bad_d}}\qquad
    \caption{Examples of days with some drops in irradiance, where the model performed badly.
    \label{fig:full_med_bad}}
\end{figure}

\clearpage
\subsection{High variance days}
A few days in the dataset had very low irradiance for part of, or the whole day or large fluctuations in irradiance. These situations were most difficult for the model to predict. Figs.~\ref{fig:full_high_a}, \ref{fig:full_high_b} and \ref{fig:full_high_c} show the model somewhat following the observations, but with a high MAPE of 38-80\% because of offsets in time and/or magnitude. The observed value was often outside the 90\% confidence interval of the predictions. For Figs.~\ref{fig:full_high_a}, \ref{fig:full_high_b} the sum of predicted values is close to the sum of observed values, indicating relatively high accuracy for the days taken as a whole. Fig.\ref{fig:full_high_d} shows an outlier with an extremely high MAPE of 139\%, where the model predicts an almost clear day, with high confidence, on a day that receives very little irradiance.
\begin{figure}[ht!]
    \centering
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/high/high_1.png}\label{fig:full_high_a}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/high/high_2.png}\label{fig:full_high_b}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/high/high_3.png}\label{fig:full_high_c}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/high/high_4.png}\label{fig:full_high_d}}\qquad
    \caption{Examples of days with large drops in irradiance or low irradiance throughout.
    \label{fig:full_high}}
\end{figure}

\clearpage
\section{Less forecast data}
The limited model, utilizing irradiance data only from the one forecast region, and not surrounding regions, achieved an average MAPE of 15.98\% on the test dataset. The maximum daily average MAPE was 122.87\% and the minimum was 3.47\%. 
\begin{figure}[ht!]
    \centering
    \includegraphics[scale=0.75]{imgs/graphs/less/days_single.png}
    \caption{The recorded Mean Absolute Percentage Error for each day in the test dataset of the limited model. 
    \label{fig:days_less}}
\end{figure}

\subsection{Low variance days}
The model predicts most clear days with relatively high accuracy, but even on the best days, it deviates quite a bit from the observed values, as shown in Fig.~\ref{fig:less_low_a}. The model sometimes under-predicts on clear days. In Fig.~\ref{fig:less_low_b} we can see an example of a day where, even though the 90\% confidence area is large, the observed irradiance is outside it.
\begin{figure}[ht!]
    \centering
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/less/low/low_g_1.png}\label{fig:less_low_a}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/less/low/low_b_1.png}\label{fig:less_low_b}}\qquad
    \caption{Examples of model performance on clear days.
    \label{fig:less_low}}
\end{figure}
poopies manana

\subsection{Medium variance days}
The model shows less accuracy when the irradiance is not steady. Predictions for most days have the smooth profile of an optimal day but are scaled to fit closer to the lower total irradiance for the day. The model is inconsistent in how well it tracks the observed irradiance and the confidence it does that with. Sometimes, as shown in Fig.~\ref{fig:less_med_a} the model tracks relatively well, with the observations mostly within the rather tight 90\% confidence interval of roughly $+50/-150 W/m^2$. In Fig.~\ref{fig:less_med_b} we see an example where the model was wrong with very high confidence for the first half of the day. Fig.~\ref{fig:less_med_c} shows the opposite, the model predicts low irradiance for the whole day with a very large 90\% confidence interval of roughly $\pm200 W/m^2$.
\begin{figure}[ht!]
    \centering
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/less/medium/med_g_1.png}\label{fig:less_med_a}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/less/medium/med_m_2.png}\label{fig:less_med_b}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/less/medium/med_m_1.png}\label{fig:less_med_c}}\qquad
    \caption{Examples of days with some drops in irradiance.
    \label{fig:less_med}}
\end{figure}

\clearpage
\subsection{High variance days}
For the few days in the dataset that had very low irradiance for part of, or the whole day or large fluctuations in irradiance, the model showed high error, MAPE in the range 53-123\% with varying confidence. Figs.~\ref{fig:less_high_a} and \ref{fig:less_high_b} show large over-predictions with high confidence, and Figs.~\ref{fig:less_high_c} and \ref{fig:less_high_d} show days where the 90\% confidence interval covered the top 60\% of the graph, yet it did not cover the observations.
\begin{figure}[ht!]
    \centering
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/less/high/high_1.png}\label{fig:less_high_a}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/less/high/high_2.png}\label{fig:less_high_b}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/less/high/high_3.png}\label{fig:less_high_c}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/less/high/high_4.png}\label{fig:less_high_d}}\qquad
    \caption{Examples of days with large drops in irradiance or low irradiance throughout.
    \label{fig:less_high}}
\end{figure}

>>>>

\chapter{Results}
Both models show a strong ability to predict solar irradiance one day into the future.
The full model, using weather forecast data from the surrounding area, shows both a lower Mean Absolute Percentage Error (MAPE), at 13.21\% vs. 15.98\%, as well as better tracking in challenging conditions and a better ability to recognize uncertain conditions, generally reporting lower confidence when its predictions are wrong. Both models can be trained to achieve slightly lower MAPE, but that comes at the cost of a higher tendency to underfit variance, and higher false confidence.
We show irradiance plots for select days representative of the models' performance in various conditions. These plots show the measured irradiance for the day, the models' predicted irradiance values, along with a 90\% confidence interval, detailed in section~\ref{sec:loss_function}. The plots also show the forecast downward shortwave irradiance, the largest factor in measured irradiance, from the model input. Additionally, the graphs contain the average MAPE for the day and the sum of prediction and observation values. The sum values act as a gauge for the total irradiance for the day.

\section{Full model}
The full model, utilizing irradiance data from surrounding areas achieves an average MAPE of 13.21\% on the test dataset. The maximum daily average MAPE is 138.87\% and the minimum is 2.50\%. Figure~\ref{fig:days_full} shows the average MAPE the full model achieves for the test dataset on a day-by-day basis.
\begin{figure}[ht!]
    \centering
    \includegraphics[scale=0.75]{imgs/graphs/full/days_full.png}
    \caption{The recorded Mean Absolute Percentage Error (MAPE) for each day in the test dataset for the full model. 
    \label{fig:days_full}}
\end{figure}

\subsection{Low variance days}
In the test dataset, there are some clear days, where the sun was mostly or entirely unobstructed. The model predicts most of these days with very low error, in the range of 2-5\%. The 90\% confidence interval stays within $\pm100 W/m^2$ for the whole day and the true prediction is almost spot-on, as can be seen in Figure~\ref{fig:full_low_best}.
\begin{figure}[ht!]
    \centering
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/low/best_3.png}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/low/best_2.png}}\qquad
    \caption{Examples of clear days where the model preforms very well.
    \label{fig:full_low_best}}
\end{figure}

The model does not manage near-perfect predictions on all of these clear days, and makes a few under-predictions, as can be seen in Figure~\ref{fig:full_low_worst}.
These predictions still predict steady sunshine, and are within the 90\% confidence interval, which is slightly larger than for the other clear day predictions. These predictions have a higher MAPE of 10-13\%.
\begin{figure}[ht!]
    \centering
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/low/worst_1.png}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/low/worst_2.png}}\qquad
    \caption{Examples of clear days where the model does not perform well.
    \label{fig:full_low_worst}}
\end{figure}

\subsection{Medium variance days}
On days with some variance in the irradiance measured, the model is generally able to predict the irradiance with relatively good accuracy.
The model tends to give a smoother prediction than the measured value, averaging through the peaks and valleys of the measured values and most of the time the observed value is within the 90\% confidence interval.

Figure~\ref{fig:full_med_best} shows examples of good predictions with high confidence, though the confidence is generally lower the farther the irradiance is from the value of a clear day.
\begin{figure}[ht!]
    \centering
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/medium/med_g_1.png}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/medium/med_g_2.png}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/medium/med_g_3.png}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/medium/med_g_4.png}}\qquad
    \caption{Examples of days with some drops in irradiance, where the model performs very well.
    \label{fig:full_med_best}}
\end{figure}

In Figure~\ref{fig:full_med_med} we see examples of days where the model achieves higher error, MAPE in the range 19-35\%, but with generally larger 90\% confidence intervals so the model still keeps the measured values close to or within them.
\begin{figure}[ht!]
    \centering
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/medium/med_m_1.png}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/medium/med_m_2.png}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/medium/med_m_3.png}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/medium/med_m_4.png}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/medium/med_m_5.png}}\qquad
    \caption{Examples of days with some drops in irradiance, where the model performs somewhat well.
    \label{fig:full_med_med}}
\end{figure}

For a few medium variance days, the model does not track well. Figures~\ref{fig:full_med_bad_a} and \ref{fig:full_med_bad_d} show where the model predicts a constant lower irradiance when half the day had high irradiance and the other half low. Figures~\ref{fig:full_med_bad_b} and \ref{fig:full_med_bad_c} show the model predicting a mostly or fully sunny day when it wasn't. In all of these cases, the observed irradiance is far outside the 90\% confidence interval.
\begin{figure}[ht!]
    \centering
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/medium/med_b_1.png}\label{fig:full_med_bad_a}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/medium/med_b_2.png}\label{fig:full_med_bad_b}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/medium/med_b_3.png}\label{fig:full_med_bad_c}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/medium/med_b_4.png}\label{fig:full_med_bad_d}}\qquad
    \caption{Examples of days with some drops in irradiance, where the model performs badly.
    \label{fig:full_med_bad}}
\end{figure}

\clearpage
\subsection{High variance days}
A few days in the dataset had very low irradiance for part of, or the whole day, or large fluctuations in irradiance. These situations are the most difficult for the model to predict. Figures~\ref{fig:full_high_a}, \ref{fig:full_high_b} and \ref{fig:full_high_c} show the model somewhat following the observations, but with a high MAPE of 38-80\% because of offsets in time and/or magnitude. The observed value is often outside the 90\% confidence interval of the predictions. For Figures~\ref{fig:full_high_a}, \ref{fig:full_high_b} the sum of predicted values is close to the sum of observed values, indicating relatively high accuracy for the days taken as a whole. Figure\ref{fig:full_high_d} shows an outlier with an extremely high MAPE of 139\%, where the model predicts an almost clear day, with high confidence, on a day that received very little irradiance.
\begin{figure}[ht!]
    \centering
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/high/high_1.png}\label{fig:full_high_a}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/high/high_2.png}\label{fig:full_high_b}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/high/high_3.png}\label{fig:full_high_c}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/high/high_4.png}\label{fig:full_high_d}}\qquad
    \caption{Examples of days with large drops in irradiance or low irradiance throughout.
    \label{fig:full_high}}
\end{figure}

\clearpage
\section{Less forecast data}
To confirm that the full model utilizes the input data for the surrounding area, we also trained the model on only irradiance forecast for the cell the power station is located in.
The limited model achieves an average MAPE of 15.98\% on the test dataset. The maximum daily average MAPE is 122.87\% and the minimum is 3.47\%. Figure~\ref{fig:days_less} shows the average MAPE the limited model achieved for the test dataset on a day-by-day basis.
\begin{figure}[ht!]
    \centering
    \includegraphics[scale=0.75]{imgs/graphs/less/days_single.png}
    \caption{The recorded Mean Absolute Percentage Error for each day in the test dataset of the limited model. 
    \label{fig:days_less}}
\end{figure}

\subsection{Low variance days}
The model predicts most clear days with relatively high accuracy, but even on the best days, it deviates quite a bit from the observed values, as shown in Figure~\ref{fig:less_low_a}. The model sometimes under-predicts on clear days. In Figure~\ref{fig:less_low_b} we can see an example of a day where, even though the 90\% confidence area is large, the observed irradiance is outside it.
\begin{figure}[ht!]
    \centering
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/less/low/low_g_1.png}\label{fig:less_low_a}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/less/low/low_b_1.png}\label{fig:less_low_b}}\qquad
    \caption{Examples of model performance on clear days.
    \label{fig:less_low}}
\end{figure}
poopies manana

\subsection{Medium variance days}
The model shows less accuracy when the irradiance is not steady. Predictions for most days have the smooth profile of an optimal day but are scaled to fit closer to the lower total irradiance for the day. The model is inconsistent in how well it tracks the observed irradiance and the confidence it does that with. Sometimes, as shown in Figure~\ref{fig:less_med_a} the model tracks relatively well, with the observations mostly within the rather tight 90\% confidence interval of roughly $+50/-150 W/m^2$. In Figure~\ref{fig:less_med_b} we see an example where the model is wrong with very high confidence for the first half of the day. Figure~\ref{fig:less_med_c} shows the opposite, the model predicts low irradiance for the whole day with a very large 90\% confidence interval of roughly $\pm200 W/m^2$.
\begin{figure}[ht!]
    \centering
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/less/medium/med_g_1.png}\label{fig:less_med_a}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/less/medium/med_m_2.png}\label{fig:less_med_b}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/less/medium/med_m_1.png}\label{fig:less_med_c}}\qquad
    \caption{Examples of days with some drops in irradiance.
    \label{fig:less_med}}
\end{figure}

\clearpage
\subsection{High variance days}
For the few days in the dataset that had very low irradiance for part of, or the whole day or large fluctuations in irradiance, the model displays high error, MAPE in the range 53-123\% with varying confidence. Figures~\ref{fig:less_high_a} and \ref{fig:less_high_b} show large over-predictions with high confidence, and Figures~\ref{fig:less_high_c} and \ref{fig:less_high_d} show days where the 90\% confidence interval covers the top 60\% of the graph, yet it does not cover the observations.
\begin{figure}[ht!]
    \centering
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/less/high/high_1.png}\label{fig:less_high_a}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/less/high/high_2.png}\label{fig:less_high_b}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/less/high/high_3.png}\label{fig:less_high_c}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/less/high/high_4.png}\label{fig:less_high_d}}\qquad
    \caption{Examples of days with large drops in irradiance or low irradiance throughout.
    \label{fig:less_high}}
\end{figure}
